\documentclass{article}
\usepackage{geometry}
\usepackage{forest}
\usepackage{fancyvrb}

\geometry{a4paper, margin=1in}
\renewcommand{\thesection}{\Alph{section}.}

\newcommand{\code}[1]{\Verb/{#1}/}

\begin{document}

{\Large Lab 12 Planning Document}
\vspace{0.25in}

\noindent
By submitting this assignment, I agree to the following: \\
\indent ``Aggies do not lie, cheat, or steal, or tolerate those who do'' \\
\indent ``I have not given or received any unauthorized aid on this assignment'' \\

\noindent
Name:        Rushil Udani, Braeden Stewart, Collin Stafford, Grant Trusty \\*
Section:     219 \\*
Assignment:  Team Project Planning Document \\*
Date:        15 11 2020 \\*

\hrulefill

\section{List of Functions}
\begin{itemize}
	\item \code{get\_basics}
		\begin{itemize}
			\item Purpose: Get user selections for bird and planet.
			\item Parameters: None
			\item Return values: \code{(bird, gravity)} where \code{bird} is an element of \code{BIRDS}, and \code{gravity} is the gravity of the planet.
			\item Other functions: \code{bird\_picker}, \code{planet\_picker}.
		\end{itemize}
	\item \code{bird\_picker}
		\begin{itemize}
			\item Purpose: Get user selection for bird.
			\item Process: Print a menu of all birds; Get user selection; Return associated bird.
			\item Parameters: None; depends on \code{BIRDS}
			\item Return values: \code{(name, color, size)}, an element of \code{BIRDS}
			\item Other functions: None
		\end{itemize}
	\item \code{planet\_picker}
		\begin{itemize}
			\item Purpose: Get user selection for planet.
			\item Process: Print a menu of all planets; Get user selection; Return associated planet.
			\item Parameters: None; depends on \code{PLANETS}
			\item Return values: \code{(name, gravity)}, an element of \code{PLANETS}
			\item Other functions: None
		\end{itemize}
	\item \code{get\_guesses}
		\begin{itemize}
			\item Purpose: Get user guesses for velocity and launch angle.
			\item Parameters: None
			\item Return values: \code{(vel, angle)}
			\item Other functions: None
		\end{itemize}
	\item \code{trajectory}
		\begin{itemize}
			\item Purpose: Calculate points along the bird's flight path.
			\item Parameters: \code{gravity}, \code{vel}, \code{angle}
			\item Return values: None
			\item Other functions: \code{trajectory\_y}
		\end{itemize}
	\item \code{hit}
		\begin{itemize}
			\item Purpose: Determine whether the target was hit or not.
			\item Parameters: \code{xs}, \code{ys}, \code{target} (given as \code{(x, y, size)})
			\item Return values: \code{bool}
			\item Other functions: None
		\end{itemize}
	\item \code{birds\_plot}
		\begin{itemize}
			\item Purpose: Plot and show a picture of the scene.
			\item Parameters: \code{xs}, \code{ys}, \code{target} (given as \code{(x, y, size)}), \code{bird} (as an element of \code{BIRDS})
			\item Return values: None
			\item Other functions: \code{hit}
		\end{itemize}
	\item \code{trajectory\_y}
		\begin{itemize}
			\item Purpose: Calculate the height of a point on a trajectory.
			\item Parameters: \code{x}, \code{gravity}, \code{vel}, \code{angle}
			\item Return values: \code{y}
			\item Other functions: None
		\end{itemize}
\end{itemize}

\section{Hierarchy for Lab12 Program 1}
\begin{forest}
	[Angry Birds Program, for tree={fill=green!20, draw=black, align=center}, for leaves={fill=blue!20}, fit=tight
		[Main Loop
			[Generate random target]
			[\code{get\_basics}
				[\code{get\_bird}]
				[\code{get\_planet}]
			]
			[Loop until bird hits target
				[\code{get\_guesses}]
				[Calculate and plot trajectory
					[\code{trajectory}]
					[\code{birds\_plot}]
				]
			]
		]
		[Exit gracefully]
	]
\end{forest}

\end{document}

